---
title: "Weather Forcasting"
author: "Mohit Abbi"
date: "3/29/2018"
output: html_document
---

Installing necessary Libraries

```{r}

library(forecast)
library(tseries)

```

Loading TempUSA data 

```{r}
Temp <- read.csv("C:/Users/Dell-pc/Desktop/Github/Projects/Weather Forecasting/TempUSA.csv", header = TRUE)
#View(Temp)
str(Temp)
summary(Temp)
```

Converting data into time series 

```{r}
temptrend<-ts(Temp, frequency=12, start =c(2000,1))
is.ts(temptrend)
str(temptrend)
Temp1=Temp$LosAngelesMin
#View(Temp1)
str(Temp1)
```

For decomposition plot, I'll use stl: seasonal trend decomposition

Make a stl object #TempLATS

```{r}
TempLATS<-ts(Temp1, frequency=12, start =c(2000,1) )
str(TempLATS)
is.ts(TempLATS)
plot(TempLATS)
class(TempLATS)
adf.test(TempLATS)
is.ts(TempLATS)
LA=stl(TempLATS,s.window = "periodic")
#LA
plot(LA)
```

Plotting ACF and PACF

```{r}
acf(TempLATS)
pacf(TempLATS)
```

Generating Prediction(For LA)

```{r}
LA.fit <- arima(TempLATS, order =c(1,1,0), seasonal = list(order = c(1,1,0), period =12), include.mean = FALSE)
LA.fit
LA.pred <- predict(LA.fit, n.ahead = 12)
plot(TempLATS,xlim=c(2000,2015), ylim=c(0,25))
lines(LA.pred$pred, col="blue")
lines(LA.pred$pred+LA.pred$se, col="RED")
lines(LA.pred$pred-LA.pred$se, col="RED")
```

Forecasting using auto.arima

```{r}
TemLA = auto.arima(TempLATS)
summary(TemLA)
forecLA = forecast(TemLA,h=20)
plot(forecast(forecLA))
```

Autocorrelation

```{r}
plot.ts(TemLA$residuals)
qqnorm(TemLA$residuals)
acf(TemLA$residuals)
```

Density Plot for LosAngeles

```{r}
TLA<-density(TempLATS)
plot(TLA)
polygon(TLA,col = "red",border="blue")
```

Hypothesis testing

One sample T-test

```{r}
# Ha: mu > 12
t.test(x=Temp$LosAngelesMin,mu=12, alternative="greater")
# Ha: mu < 12
t.test(Temp$LosAngelesMin, mu=12, alternative="less")
```

Proportion Test

```{r}
prop.test(x=10, n=154, p = 0.3)
prop.test(x=90, n=154, p=0.5)
prop.test(x=90, n=154,p=0.5,alternative = "greater")
```
